### 2014-05-09 tex/main-body-text.tex
Some minor additions to flock method description.

\subsection*{{\sc flock}}
Here we translate the recipe given by \citeauthor{Duc&Tur2009} for the 
{\sc flock} algorithm into a concise specification in terms of the variables
defined in the previous section.  We provide the description for case when
it is assumed there are $K$ clusters.

The first step of the flock algorithm is initialization.  [Now echo what the
authors say about this, and then translate that into an equation on $Z_i$]

@@

\subsection*{{\sc flock} analysis of coasta California steelhead} 
{\sc flock} was run four times using the default setting for all run parameters 
\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. 
Run times were relatively short. The four groups of runs for the default settings 
averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no 
plateaus were observed in any of the four groups for a \textit{k} greater than two, 
the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). 
The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to two different 
conclusions for the plateau sequences observed: \textit{k}=2 is the lower bound 
estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite 
different conclusions, the allocation of individuals for the 'best run' from each 
group differed by a only a single individual. When \textit{k}=2, {\sc flock} 
identifies a boundary in the Russian Gulch area clustering individuals into northern 
and southern groups (Fig. 1).

>>>>

\subsection*{{\sc flock}}
Here we translate the recipe given by \citeauthor{Duc&Tur2009} for the 
{\sc flock} algorithm into a concise specification in terms of the variables
defined in the previous section.  We provide the description for a case in which
it is assumed there are $K$ clusters.

The first step of the flock algorithm is initialization, during which 
the program randomly allocates each of the $N$ individuals to one of 
$K$ clusters.  Then a number of reallocation steps are performed.  During every one of 
these steps, each individual is given the chance to be reallocated 
(\ie moved to a different cluster).  This is done on the basis of 
maximum likelihood:

@@

\subsection*{{\sc flock} analysis of coastal California steelhead} 
{\sc flock} was run four times using the default setting for all run parameters 
\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. 
Run times were relatively short. The four groups of runs for the default settings 
averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no 
plateaus were observed in any of the four groups for a \textit{k} greater than two, 
the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). 
The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to two different 
conclusions for the plateau sequences observed: \textit{k}=2 is the lower bound 
estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite 
different conclusions, the allocation of individuals for the 'best run' from each 
group differed by a only a single individual. When \textit{k}=2, {\sc flock} 
identifies a boundary in the Russian Gulch area clustering individuals into northern 
and southern groups (Fig. 1).
